---
title: "SetSysVis"
author: "Vignette Author"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
set.seed(666)
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
library(SetSysVis)
library(GGally)
```


## Generating a set

First, we need to generate a set system we want to visualize. To do this we use function `generateClosedFamily`.

```{r, fig.width=6, fig.height=6}
A <- generateClosedFamily(6, 6)
knitr::kable(A)
```

We want to generate names vector for our system as well.

```{r}
names <- generateNamesVector(A)
```

## Generating matrices

We can generate four types of matrices

```{r}
M1 <- generateCommonElementMatrix(A)
M2 <- generateInclusionMatrix(A)
M3 <- generateInclusionTreeMatrix(A)
M4 <- generateDisjointTrees(A)
```

## Visualization

To visualize the set we need the package `GGally`. The first three matrices are simple.

```{r, fig.width=6, fig.height=6}
ggnet2(M1, label = names)
```
```{r, fig.width=6, fig.height=6}
ggnet2(M2, label = names)
```
```{r, fig.width=6, fig.height=6}
ggnet2(M3, label = names)
```

When it comes to the fourth matrix, the function returns a two-element list of a matri and vector of colors, to make the sets more distinguishable.

```{r, fig.width=6, fig.height=6}
ggnet2(M4[[1]], label = rownames(M4[[1]]), color = M4[[2]])
```